%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[svgnames, 10pt, a4paper]{article}
\usepackage{fontspec} 

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
%\usepackage[usenames,dvipsnames]{color}
\usepackage{xcolor}
\usepackage{xltxtra}
\usepackage{xunicode}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
\setmonofont[Scale=0.8]{Monaco}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% ---- ENVIRONMENTS
\newenvironment{nstabbing}
  {\setlength{\topsep}{0pt}%
   \setlength{\partopsep}{0pt}%
   \tabbing}
  {\endtabbing}

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize} 
\subsubsectionfont{\mdseries\upshape\large} 

% PDF SETUP
% Here, removed dvi driver options ``dvipdfm"
\usepackage[bookmarks, colorlinks, breaklinks, 
	pdftitle={Eric R. J. Edwards - cv},
	pdfauthor={erje},
	pdfproducer={}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} 

% DOCUMENT
\begin{document}
{\LARGE Eric R. J. Edwards}\\[1cm]
\begin{minipage}{0.5\textwidth}
\begin{flushleft} Institut für Angewandte Physik\\
Corrensstraße 2-4\\
\texttt{48149} Münster\\
%Germany\\[.2cm]
Germany\\
\end{flushleft}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\begin{flushleft}
email: \href{mailto:eedwa_01@uni-muenster.de}{eedwa\_{}01@uni-muenster.de}\\
\textsc{url}: \href{http://www.uni-muenster.de/Physik.AP/Demokritov/Organisation/Mitglieder/edwards.shtml}{Ins. f. Ang. Phy.}\\ 
%\vfill
\begin{nstabbing}
\textsc{t}\= : \texttt{+49 251 83-33550}\\
\textsc{f}\> : \texttt{+49 251 83-33513}
\end{nstabbing}
\end{flushleft}
\end{minipage}\\[.2cm]
Born:  July 25, 1987---Washington D.C., USA\\
Nationality:  American

%\hrule
\section*{Education}
\noindent
\years{2012}\textbf{\textsc{PhD} in Physics} {\footnotesize (anticipated)}\\
\emph{Westfälische-Wilhems Universität}, Germany\\
\textsc{Advisor: Prof. Dr. S. O. Demokritov}\\
\years{2009}\textbf{\textsc{BSc} in Physics}  {\footnotesize (summa cum laude)}\\
\emph{Universtiy of Alabama}, U.S.A.

\section*{Academic Work}

\subsection*{Journal articles}
\noindent
%
\years{2012}E. R. J. Edwards, Matthias Buchmeier, V. E. Demidov, and S. O. Demokritov,\\ “Magnetostatic spin-wave modes of a tangentially magnetized disc",\\ \emph{preprint}\\
%
\years{2011}V. E. Demidov, S. Urazhdin, E. R. J. Edwards, and S. O. Demokritov,\\ “Wide-range control of ferromagnetic resonance by spin Hall effect",\\ \emph{Appl. Phys. Lett.} \textbf{99}: 172501 (2011)\\ 
%
\years{2011}V. E. Demidov, S. Urazhdin, E. R. J. Edwards, M. D. Stiles, R. D. McMichael, and S. O. Demokritov,\\ “Control of Magnetic Fluctuations by Spin Current",\\ \emph{Phys. Rev. Lett.} \textbf{107}: 107204 (2011)\\ 
%
\years{2010}T. Mewes, R.L. Stamps, H. Lee, E. Edwards, M. Bradford, C.K.A. Mewes, Z. Tadisina, S. Gupta,\\ “Unidirectional magnetization relaxation in exchange-biased films",\\ \emph{IEEE Magnetics Letters} \textbf{1}: 5550119 (2010)

\subsection*{Talks}
\noindent
\years{2011}Deutsche Physikalische Gesellschaft Frühjahrstagung, ``Spin-wave spectrum of a YIG disc"\\
\years{2008}American Physical Society March Meeting, ``Non-local damping effects in Py-Cu-FeMn trilayers"

\subsection*{Other Work}
\noindent
\years{2009}Karyn Kupcinet Summer School for International Students\\
\emph{Weizmann Institute of Science}. Rehovot, Israel.\\
\textsc{Advisor: Prof. Moty Heiblum}\\
%Report: ``Superconducting contacts to a two-dimensional electron gas in AlGaAs/GaAs heterostructures"\\
Report: ``Superconducting contacts to a 2D electron gas in AlGaAs/GaAs heterostructures"\\
%
\years{2008}National Science Foundation R.E.U.\\ 
\emph{Cornell Laboratory for Elementary Particle Physics}. Ithaca, New York.\\
\textsc{Advisor: Prof. Georg Hoffstaetter}\\
Report: ``Time of Flight Identification of Ions in CESR and ERL Beam Pipes"\\
%
\years{2007}National Science Foundation R.E.U.\\
\emph{Columbia University Department of Applied Physics}. New York City, New York.\\
\textsc{Advisor: Prof. William Bailey}\\
Report: ``Low relaxation rates in doped ultrathin iron films"

\section*{Grants, honors \& awards}
\noindent
\years{2008}Barry M. Goldwater Scholarship\\
%\years{2008}Outstanding Senior Physics Student\\
\years{2005}E. Scott Barr Scholarship in Physics

\section*{Languages}
\emph{English} (native speaker)\\
\emph{German} (professional proficiency)

\section*{References}
\noindent
Prof. Dr. Sergej Demokritov\\
Institut für Angewandte Physik\\
Correnstraße 2-4\\
\texttt{48149} Münster\\
Germany\\
\href{mailto:demokrit@uni-muenster.de}{demokrit@uni-muenster.de}
\begin{nstabbing}
\textsc{t}\= : \texttt{+49 251 83-33551}\\
\textsc{f}\> : \texttt{+49 251 83-33513}\\[.2cm]
\end{nstabbing}
\noindent
Dr. Tim Mewes\\
University of Alabama\\
Department of Physics \& Astronomy\\
Box 870209\\
Tuscaloosa, AL \texttt{35487}\\
U.S.A.\\
\href{mailto:tmewes@ua.edu}{tmewes@ua.edu}
\begin{nstabbing}
\textsc{t}\= : \texttt{+1 205-348-9187}\\
\textsc{f}\> : \texttt{+1 205-348-2346}
\end{nstabbing}
\vfill
\begin{center}
{\scriptsize  Last updated: \today\- •\- 
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://nitens.org/taraborelli/cvtex}{
\fontspec{Times New Roman}\XeTeX }\\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
\href{http://github.com/erje/cv}{http://github.com/erje/cv}}
\end{center}

\end{document}
